MassWateR: Improving Quality Control, Analysis, and Sharing of Water Quality Data

### 2023-08-20 manu-draft.qmd
changing fig imports to markdown only, filerequirements table is now kable

execute: 
  echo: false
  warning: false
  message: false
  ft.keepnext: false
  ft.align: left
---

@@

library(flextable)
library(officer)
library(officedown)
library(dplyr)
library(here)

flextable::set_flextable_defaults(font.size = 7, padding = 0)

@@

```{r}
#| label: fig-workflow
#| fig-cap: 'Workflow demonstrating how a user could engage with the *MassWateR* package. WQX: Water Quality Exchange; QC: Quality Control.'
#| fig-alt: 'Workflow diagram showing four ways to engage with *MassWateR*'
#| out-width: '100%'
knitr::include_graphics('figs/workflow.png')
```

@@

The required data files for using *MassWateR* are shown in `r run_reference(id = "tbl-filreq")`, including how each file applies to the workflow steps in @fig-workflow.  The files are imported into R using specific `read` functions with relevant checks, explained in the next section.  These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a formatting issue.  The largest input file required for all parts of the workflow in @fig-workflow is the results file.  This file includes all water quality monitoring data to be used with the package and the recommendation is that the results data include a year of sampling as reporting typically follows an annual cycle. The results file design also considered WQX requirements to facilitate data submission. As such, the formatting requirements for the results file are the most burdensome for potential users and additional functions are available to assist in this effort.

```{r}
#| label: tbl-filreq
#| tbl-cap: 'File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow. DQO: Data Quality Objective; QC: Quality Control.'
filerequirements
```

@@

```{r}
#| label: fig-importflow
#| fig-cap: "Pseudocode demonstrating the iterative process of importing a required data file for *MassWateR*.  All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`)."
#| fig-alt: 'Diagram showing pseudocode for importing and fixing a data file with *MassWateR*'
#| out-width: "100%"
knitr::include_graphics('figs/importflow.png')
```

>>>>

execute: 
  echo: false
  warning: false
  message: false
---

@@

library(dplyr)
library(here)

@@

![Workflow demonstrating how a user could engage with the *MassWateR* package. WQX: Water Quality Exchange; QC: Quality Control.](figs/workflow.png){#fig-workflow width=100% fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}

@@

The required data files for using *MassWateR* are shown in @tbl-filreq, including how each file applies to the workflow steps in @fig-workflow.  The files are imported into R using specific `read` functions with relevant checks, explained in the next section.  These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a formatting issue.  The largest input file required for all parts of the workflow in @fig-workflow is the results file.  This file includes all water quality monitoring data to be used with the package and the recommendation is that the results data include a year of sampling as reporting typically follows an annual cycle. The results file design also considered WQX requirements to facilitate data submission. As such, the formatting requirements for the results file are the most burdensome for potential users and additional functions are available to assist in this effort.

```{r}
#| label: tbl-filreq
#| tbl-cap: 'File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow. DQO: Data Quality Objective; QC: Quality Control.'
knitr::kable(filerequirements)
```

@@

![Pseudocode demonstrating the iterative process of importing a required data file for *MassWateR*.  All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](figs/importflow.png){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width=100%}
